A Sound Deep Embedding of Arbitrary Normal Modal Logics in Coq

### 2022-06-21 paper/paper.tex
Non pushed changes to paper

@@

In this work, we presented a sound deep embedding of arbitrary
normal modal logics in Coq. Our approach is able to represent uniformly
deduction over different modal logic systems by using different axiom sets
as a predicate parameter in the deduction inductive type. Using this generic
representation of deduction we are able to prove the soundness theorem and
apply it on proving L\"ob's theorem.

As future work we intend to prove the completeness result for the Hilbert
deduction system, including support for multimodalities (fusion of modal logics)
and non-normal modal logic systems.

>>>>

All source code in this article has been formalized in Coq version 8.15.0 and it
is available at~\cite{modal-coq-lib}.

@@

In this work, we presented a sound deep embedding of arbitrary
normal modal logics in Coq. Our approach is able to represent uniformly
deduction over different modal logic systems by using different axiom sets
as a predicate parameter in the deduction inductive type. Using this generic
representation of deduction we are able to prove the soundness theorem and
apply it on proving L\"ob's theorem. All source code in this article has
been formalized in Coq version 8.15.0 and it is available at~\cite{modal-coq-lib}.

As future work we intend to prove the completeness result for the Hilbert
deduction system and continue the development of our library by including
support for multimodalities (fusion of modal logics) and non-normal modal
logic systems.
